Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update ASC results
some revisions before Eq 12

with $c_N$ the $N$'th nearest neihgbor of the centroid $c_i$, and $\parallel \bullet \parallel$ the euclidean norm.

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
ei (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
ei (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
li (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
li (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-c         & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-a         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-w         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{...}
\end{center}
\end{table}

>>>>

where $c_N$ is defined as the $N^{\textrm{th}}$ nearest neighbor of the centroid $c_i$, and $\parallel \cdot \parallel$ denotes the Euclidean norm.

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
ei (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
ei (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
li (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
li (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-c         & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-a         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-w         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{FYW: best results for object-based approach with majority vote (on the centroids / on the centroids + on the frames) is circa 75\%}
\end{center}
\end{table}
